---
title: "Deisotoper: Tutorial"
author: "Lucas Schmidt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Installation

## Needed software

- Java JDK 8 (64 bit)
- R 3.4.2 (64 bit)


## Additional software

- R Studio (64 bit)


## Installation

First install the dependencies.

```{r eval=FALSE}
install.packages(c('rJava', 'devtools', DiagrammeR, lattice, roxygen2, protViz, shiny, testthat, mzR, knitr))
```

Then use the deisotoper_0.0.1.tar.gz file to install the deisotoper package.

```{r eval=FALSE}
install.packages("~/deisotoper_0.0.1.tar.gz", repos = NULL, type = "source")
```


# Usage

## Creating a MassSpectrometryMeasurement or MassSpectrum Java-Object

## Deisotoping a MassSpectrometryMeasurement or MassSpectrum Java-Object

## Getting the data back in R from a MassSpectrometryMeasurement or MassSpectrum Java-Object

## Getting a IsotopicClusterGraph as DOT-graph

## Analizing data

### Make a summary of a MassSpectrometryMeasurement or MassSpectrum Java-Object

### Make a statistic a MassSpectrometryMeasurement Java-Object

# Examples

